Influence of Connectivity on Dung Beetle Communities

### 2025-02-26 corridor_docs/eric_ms_thesis/thesis_planning.Rmd
thesisi planning and some rarefaction

As human disturbances continue to expand into natural landscapes, intact habitats are becoming increasingly fragmented. This degradation lends to loss in biodiversity on a global scale and interruptions in ecosystem processes and functions [@haddad_habitat_2015]. Effects from isolation can vary, however as habitats are broken down community structures are significantly altered [@WOS:000419965700012]. Corridors have been shown to be an important mechanism for facilitating the movement of organisms through fragmented landscapes with the goal of minimizing negative consequences of fragmentation[@haddad_corridor_2003].

What?

Connectivity and fragmentation 
understanding how movement corridors effect populations dung beetles 
Dispersal ability

Why?

Understanding responses to landscape change allows us to anticipate how environments might change with further disturbance. 
Patterns in population distributions might suggest how we can study focal organisms in the future.
Could help understand how interactions may be changing.

@@

How corridors directly impact dung beetle communitites

are changes driven by dispersal ability

@@

@@

# RESULTS
git config --global user.email "you@example.com"
some summary statistics:

@@

### Dedication 
Your dedication is typed here. It should begin with the word “To.” (To my Mom is a typical dedication) If your dedication is longer than a single line it should be single-spaced, and centered vertically and horizontally

>>>>

As human disturbances continue to expand into natural landscapes, intact habitats are becoming increasingly fragmented. This degradation lends to loss in biodiversity on a global scale and interruptions in ecosystem processes and functions [@haddad_habitat_2015]. Effects from isolation can vary, however as habitats are broken down community structures are significantly altered [@WOS:000419965700012]. Corridors have been shown to be an important mechanism for facilitating the movement of organisms through fragmented landscapes with the goal of minimizing negative consequences of fragmentation[@haddad_corridor_2003]. As disturbance continues to intensify, it is becoming increasingly more important to understand how different taxonomic groups. Here, we aim to gain an understanding of how dung beetles, a group of insects well known for strong dispersal ability in order to compete for ephemeral resources(Hanski and Cambefort 1991), interact with corridors in their landscapes.

@@

How corridors directly impact dung beetle communitites
are changes driven by dispersal ability

Dung beetles are an incredibly well studied group of insects which play an important role in providng ecosystem services for dung removal, secondary seed distribution, and even suppressing populations of parasitic pests[@shepherd_dung_1998; @WOS:000369463100010]. Studies have also focused on how landscape structures alter community compositions[@WOS:000398662200001], yet direect

@@

Insert description above of individual trap

@@

# RESULTS
some summary statistics:

@@

### Dedication 
To my family who never stopped supporting me along this journey, my friends who kept me company along the way, and my mentors at VCU who believed in me before I did myself.
